Manuscript Figures for Genome Biology

### 2018-05-02 manuscript_figures/manuscript_figures.Rmd
Add one-color version of Fig4 heatmap

@@

Fig4
ggsave(file.path(outdir, "Figure4.pdf"), width=6, height=4, dev = pdf)
```

>>>>

# Figure 3

@@

Fig4
ggsave(file.path(outdir, "Figure4.pdf"), width=6, height=4)

# heatmap : rows method, cols casestudy- one color scale 
Fig4alt <- Fig4 +
  scale_fill_gradient(low = "white", high = "red", na.value=NA) +
  theme(panel.background = element_rect(colour="grey60", fill="grey60",
                                        size = 0.5),
        panel.grid.major = element_line(colour = "grey60"), 
        panel.grid.minor = element_line(colour = "grey60"))

Fig4alt
ggsave(file.path(outdir, "Figure4alt.pdf"), width=6, height=4)

##
## AR: alternative suggestion to heatmap, feel free to discard! ##
##
ranks_avg$method <- factor(ranks_avg$method,
                           levels=rev(unique(ranks_avg$method[order(ranks_avg$meta_rank)])))
Fig4b <- ggplot( ranks_avg, aes(x=method, y=mean_rank, group=casestudy, col=casestudy) ) +
  geom_line() + geom_point() +
  labs(y="Mean rank", x="", col="Case study") +
  theme(axis.text.x=element_text(angle=25, vjust=1, hjust=1))
Fig4b
```
